\documentclass[12pt]{article}
\begin{document}
\begin{titlepage}
\begin{center}
\huge{\bfseries HOW TO BUILD CONFIDENCE AROUND A GIRL FOR THE FIRST TIME}\\
\end{center}
\begin{flushright}
\textsc{\LARGE SEGAWA DAVID BISASO\\
214001060\\
14/U/1115\\}
\end{flushright}
\end{titlepage}
\section{INTRODUCTION}
Feeling confident around girls is something many guys struggle with, but it doesn’t mean you are destined to a lifetime of loneliness. Being shy creates a reluctance to engage socially for fear of becoming embarrassed. Overcoming shyness is about putting your focus and energy outward during a conversation with a girl. If you work to control your feelings of shyness, and then take steps to build your confidence, you can be the life of the party.
\section{BODY}
\subsection{Dress to impress.}
It is important that you feel good about your clothing and style to present yourself in the best light. It doesn’t matter what you wear as long as it feels good to you. There is no one style that says “I’m confident,” but if you believe that you wear it well, you will!
\subsection{Educate yourself on topics you’re interested in}
Being able to discuss a topic in detail will give you the confidence to begin a conversation with many different people. Learn more than just the headlines of a news story and you can discuss the details with several groups of individuals.
\subsection{Make eye contact when speaking to someone}
Communication is about so much more than words. Sometimes what we say is less important that how we say it. Make sure that you are letting the people you talk to know you care about them by connecting with them visually throughout your conversation.
\subsection{Set easy goals for yourself.}
Start off by making a point to say “Hi” to a girl you want to talk to. Open the door for future conversations by taking small steps. Don’t expect to be the head cheerleader’s best friend if you’ve never talked to her before. You need to build up confidence by introducing yourself to lots of people to get comfortable talking to lots of girls.
\subsection{Practice talking in the mirror.}
Watch your facial expressions and think about what responses you would have in a particular conversation. Knowing what you might say can help you prepare for a great conversation. Just a simple smile at yourself each day can do wonders for your self esteem!
\subsection{Be honest about your shyness.}
When you introduce yourself to a girl, let her know that you are trying to overcome being shy. Many girls find guys who are shy extremely attractive. Let your shyness be a way in and not something that keeps you out. Try one of these opening lines:
    "There's so many people here, it's hard to find someone to talk to because I'm kinda shy."
    "Can I sit with you, I'm shy and just need a quiet place to relax."
    "I'm terrible at meeting new people, can we pretend we know each other so it isn't so awkward?"
\subsection{Make a joke about being shy.}
When you are having a conversation use the fact that you are shy as a way to poke fun at yourself.

    "Being shy always makes me feel small, do I look little to you?
    "I would tell you a joke, but I'm too shy and always mess up the punch lines"
    "If I weren't shy it would be a lot easier to find out what you like"
\subsection{Bring a friend to be your wingman.}
Sometimes having a friend by your side can make it much easier to approach a girl. Ask a friend you trust to help introduce you to new people and start conversations.
\subsection{Live in the moment.}
 Don't worry about what might happen in the future of your conversation; focus on the here and now. It is easier for the conversation to flow if you are concentrating on the current topic and not planning the future.
 \section{CONCLUSION}
 Now that you have read and understood the above points, its time now to go and approach any girl of your choice. Remember those beautiful girls are lonely and are busy waiting for you guys to go and approach them. At first she may pretend not to be interested but by your confidence around her will put you into the game.
\end{document} 